Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-03-21 paper/paper.tex
Tweaks

\usepackage{showframe}

@@

\begin{abstract}
    The maximum common subgraph problem is to find the largest subgraph common to two given graphs.
    This problem can be solved either by constraint-based search, or by reduction to the maximum
    clique problem. We evaluate these two approaches using modern algorithms. We also propose a
    restricted branching technique for the connected version of the problem, and show how to
    implement this in constraint-based and clique-inspired algorithms.
\end{abstract}

@@

\begin{algorithm}[tb] \DontPrintSemicolon
\nl $\FuncSty{cliquishMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
\nl \Begin{
    \nl $\KwSty{global} ~ C_{\mathit{max}} \gets \emptyset$ \;
    \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
    \nl $\FuncSty{expand}(G, \operatorname{V}(G), \emptyset, \emptyset)$ \;
    \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;
}
\vspace{1ex}
\nl $\FuncSty{expand}$ :: (Graph $G$, Set $C$, Set $A$, Set $P$) \;
\nl \Begin{
    \nl $\mathit{colourClasses} \gets \FuncSty{colour}(G, A, P)$ \;
    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$}{
        \nl \ForEach{$v \textnormal{~in~} \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$}{
            \nl \lIf{$|C| + \FuncSty{length}(\mathit{colourClasses}) \leq |C_{\mathit{max}}|$}{\KwSty{return}}
            \nl \lIf{$v \notin A ~ \KwSty{and} ~ C \ne \emptyset$}{\KwSty{return}}
            \nl $C' \gets C \cup \{ v \}$\;
            \nl \lIf{$|C'| > |C_{\mathit{max}}|$}{$C_{\mathit{max}} \gets C'$}
            \nl $A' \gets A \cup \FuncSty{connected}(v)$ \;
            \nl $P' \gets P \cap \operatorname{N}(G, v)$ \;
            \nl \lIf{$P' \neq \emptyset$}{$\FuncSty{expand}(G, C', A', P')$}
         }
         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
     }
}
\vspace{1ex}
\nl $\FuncSty{colour}$ :: (Graph $G$, Set $A$, Set $P$) $\rightarrow$ List of List of Vertex \;
\nl \Begin{
    \nl $\KwSty{return}$ a greedy colouring of $P \setminus A$, followed by a greedy colouring of $P
    \cap A$, both using static degree order in $G$ \;
}
\caption{A clique-inspired algorithm for MCCIS.}
\label{algorithm:mc}
\end{algorithm}

>>>>

% \usepackage{showframe}

@@

\begin{abstract}
    The maximum common subgraph problem is to find the largest subgraph common to two given graphs.
    This problem can be solved either by constraint-based search, or by reduction to the maximum
    clique problem. We evaluate these two approaches using modern algorithms. We also propose a
    restricted branching approach for the connected version of the problem,
    show how to implement this in constraint-based and clique-inspired
    algorithms, and compare it to conventional propagation.
\end{abstract}

@@

\begin{algorithm}[tb] \DontPrintSemicolon
\nl $\FuncSty{cliquishMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
\nl \Begin{
    \nl $\KwSty{global} ~ C_{\mathit{max}} \gets \emptyset$ \;
    \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
    \nl $\FuncSty{expand}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \;
    \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;
}
\vspace{1ex}
\nl $\FuncSty{expand}$ :: (Graph $G$, Set $C$, Set $A$, Set $P$) \;
\nl \Begin{
    \nl $\mathit{colourClasses} \gets \FuncSty{colour}(G, A, P)$ \;
    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$}{
        \nl \ForEach{$v \textnormal{~in~} \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$}{
            \nl \lIf{$|C| + \FuncSty{length}(\mathit{colourClasses}) \leq |C_{\mathit{max}}|$}{\KwSty{return}}
            \nl \lIf{$v \notin A ~ \KwSty{and} ~ C \ne \emptyset$}{\KwSty{return}}
            \nl $C' \gets C \cup \{ v \}$\;
            \nl \lIf{$|C'| > |C_{\mathit{max}}|$}{$C_{\mathit{max}} \gets C'$}
            \nl $A' \gets A \cup \FuncSty{connected}(v)$ \;
            \nl $P' \gets P \cap \operatorname{N}(G, v)$ \;
            \nl \lIf{$P' \neq \emptyset$}{$\FuncSty{expand}(G, C', A', P')$}
         }
         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
     }
}
\vspace{1ex}
\nl $\FuncSty{colour}$ :: (Graph $G$, Set $A$, Set $P$) $\rightarrow$ List of List of Vertex \;
\nl \Begin{
    \nl $\KwSty{return}$ a greedy colouring of $P \setminus A$, followed by a greedy colouring of $P
    \cap A$, both using static degree order in $G$ \;
}
\caption{A clique-inspired algorithm for MCCIS.}
\label{algorithm:mc}
\end{algorithm}
